Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
speeling

Having produced a schedule that minimises boat changes, we then minimise criteria 6, imbalance. Assuming the first stage produced a schedule with $\beta$ boat changes we post this as a hard constraint in stage 2, i.e.\ $\totalBoatChanges \leq \beta$. For each skipper $\sigma$ we introduce a zero/one variable $position[{i,j}]$  (\ref{posA}) which is 1 if and only if skipper $\sigma$ is in a match in time $m.j + i$, i.e.\ in the $i^{th}$ match of the  $j^{th}$ flight (\ref{posB}). Imbalance is then computed via (\ref{imbA}) for each position, as the absolute amount of over or under expected presence in a given postion. Finally, (\ref{imbB}) we compute the maximum imbalance over all positions for this skipper.

>>>>

Having produced a schedule that minimises boat changes, we then minimise
criteria 6, imbalance. Assuming the first stage produced a schedule with
$\beta$ boat changes we post this as a hard constraint in stage 2, i.e.\
$\totalBoatChanges \leq \beta$. For each skipper $\sigma$ we introduce a
zero/one variable $position[{i,j}]$  (\ref{posA}) which is 1 if and only if
skipper $\sigma$ is in a match in time $m \cdot j + i$, i.e.\ in the $i^{th}$ match
of the  $j^{th}$ flight (\ref{posB}). Imbalance is then computed via
(\ref{imbA}) for each position, as the absolute amount of over or under
expected presence in a given position. Finally, (\ref{imbB}) we compute the
maximum imbalance over all positions for this skipper.
